Supporting ecological decision making using feature-selection and variable importance

### 2019-08-05 code/98-paper/journal/manuscript.tex
save state

\begin{itemize}
	\item Do different environmental feature sets show substantial differences in performance when predicting defoliation at trees?
    \item How are various feature-selection methods influencing the predictive performance of the models?
	\item Which features are most important and how can these be interpreted in an ecological context?
\end{itemize}

@@

\begin{figure} [t!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=\textwidth] {study_area_hyperspectral.pdf}}
		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}
		\label{fig:study_area}
	\end{center}
\end{figure}

>>>>

\begin{itemize}
	\item Do different environmental feature sets show substantial differences in performance when predicting defoliation at trees?
    \item Does the combination of feature sets have an substantial effect on predictive performance?
    \item How are various feature-selection methods influencing the predictive performance of the models?
	\item Which features are most important for the models and how can these be interpreted in an ecological context?
\end{itemize}

@@

\begin{figure} [t!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=\textwidth] {study-area-hyperspectral.pdf}}
		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}
		\label{fig:study_area}
	\end{center}
\end{figure}
